---
title: "TIFF in the regions of England 2021"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: rgovspeak::govspeak
params:
    working_year:
      label: 'Year of TIFF'
      value: 2021
      input: slider
      min: 2000
      max: 2050
      step: 1
    pubdate:
     label: 'Publication date:'
     input: date
     value: !r Sys.Date()
    run:
     label: 'Run for development, figures or markdown text'
     input: select
     value: 'Development'
     choices: ['Development', 'Figures', 'Text']
---

```{r setup, include=FALSE}
if(!require(pacman)) {
  install.packages('pacman')
  library(pacman)
}

#load other packages
p_load(tidyverse, 
       glue, 
       fs, 
       readxl, 
       cli,
       scales,
       gridExtra,
       knitr,
       lubridate,
       janitor,
       here,
       ggfbs,
       xlsx)

knitr::opts_chunk$set(echo = FALSE)

working_year <- params$working_year

previous_year <- working_year - 1

pubday <- format(params$pubdate, '%d')
pubmonth <- format(params$pubdate, '%B')
pubyear <- format(params$pubdate, '%Y')
publication_date <- glue('{pubday} {pubmonth} {pubyear}')
date_pub <- format(params$pubdate,'%d%b%y') %>%
  str_to_lower()

source(here('TIFF in the regions of England in 2021', 'scripts', 'prep_data_regional.R'))
source(here('TIFF in the regions of England in 2021', 'scripts', 'functions_regional.R'))
source(here('TIFF in the regions of England in 2021', 'scripts', 'graphs_main_regional.R'))
source(here('TIFF in the regions of England in 2021', 'scripts', 'misc_main_regional.R'))
```

This publication contains the summary of the farm accounts in the regions of England for 2021 and will address trends for the ITL1 regions, this has been published alongside more detailed data sets for each of the respective ITL1 regions[^1] which further breaks down the data to ITL2 level.

Total Income from Farming (TIFF) is the income to those who own businesses within the agricultural industry. It is the total profit from all UK farming businesses on a calendar year basis. It measures the return to all entrepreneurs for their management, inputs, labour and capital invested. The term ‘income’ used throughout this notice refers to TIFF.

#### User feedback
We want to improve our understanding of how people use our TIFF publications and how we can improve them to better meet user needs. Please take the time to complete a short feedback form to help us better understand user needs. 

[User feedback form](https://docs.google.com/forms/d/1f0lVRIF5tqWKsqGCX_eyj7QqAyF0fo99YQUPbUwdFnU/edit)

## Section 1: Key messages

* 

* 

* 

#### Figure 1.1: TIFF in `r working_year` in each ITL1 region of England (£ million)
```{r}
itl1_code_to_name(tiff_itl1) %>%
  arrange(desc(.[[3]])) %>% 
  mutate_if(is.numeric, round, digits = 1) %>% 
  rename("ITL1 region name" = itl1_name) %>% 
  kable()
```
{barchart}

* 

*  

* 

#### Figure 1.2: TIFF in `r working_year` per hectare in each ITL1 region of England (£/ha)
```{r}
itl1_code_to_name(tiff_per_ha_itl1) %>%
  arrange(desc(.[[3]])) %>% 
  mutate_if(is.numeric, round, digits = 1) %>% 
  rename("ITL1 region name" = itl1_name) %>%
  kable()
```
{barchart}

* 

* 

## Section 2: Outputs and subsidies
Below is a summary of the key points regarding outputs and subsidies at the ITL1 level. Any comparison made here between current and past years is made using current prices data as this is widely considered to be the most intuitive and helpful for year on year change.

### 2.1 Overview

#### Figure 2.1

```{r 1-oututs_and_subsidies_overview}
outputs_and_subsidies_overview
```

Figure 2.1 shows the breakdown of the outputs from the agricultural industry across the last 6 years by percentage between: crops, livestock, other agricultural activities and inseparable non-agricultural activities. Total livestock output was the largest output of 5 of the 8 ITL1 regions with total crop output being the highest in the other 3. Direct payments made up between 7.2% and 10.6% of total outputs for the ITL1 regions.

$D
[Download 'Total Income from Farming in the regions of England at ITL1' (ODS, MB)]()
$D

### 2.2 Crops

#### Figure 2.2
```{r}
kable(top3_crops_itl1_across)
```
{barchart}

* 

* 

$D
[Download 'Total Income from Farming in the regions of England at ITL1' (ODS, MB)]()
$D

### 2.3 Livestock

#### Figure 2.3
```{r}
kable(top3_livestock_itl1_across)
```
{barchart}

* 

* 

$D
[Download 'Total Income from Farming in the regions of England at ITL1' (ODS, MB)]()
$D

### 2.4 Other outputs and subsidies<sup>(a)(b)</sup>

#### Figure 2.4
```{r}
kable(past_2_years_other_outputs_years_across)
```
{barchart}

<sup>(a)</sup>Since 2012, subsidies linked to production have only been paid in Scotland.

<sup>(b)</sup>Subsidies not linked to production are all subsidies not directly linked to production, including the basic payment scheme and agri-environment schemes.

The subsidies as a percentage of TIFF for each of the regions is shown below in Table X.

#### Figure 2.5
``` {r}
pub_subsidies_percentage <- itl1_code_to_name(subsidies_percentage) %>% 
  rename("ITL1 name" = itl1_name) %>% 
  rename(Value = value)

kable(pub_subsidies_percentage)
```

## Section 3: Inputs and costs

### 3.1 Overview

#### Figure 3.1

```{r 2-inputs_and_costs_overview}
inputs_and_costs_overview
```

Figure 3.1 shows the breakdown of the costs from the agricultural industry in 2021 by percentage between: intermediate consumption, total fixed capital consumption, compensation of employees, rent and other costs.The order of costs from largest to smallest is the same across all of the ITL1 regions of England as was: intermediate consumption, total fixed capital consumption, compensation of employees, rent and other costs. Intermediate consumption made up between 67.2% and 71.3% of total costs and employment costs made up between 8.9% and 13.1% in the ITL1 regions of England.

$D
[Download 'Total Income from Farming in the regions of England at ITL1' (ODS, MB)]()
$D

Due to the differences between each region and the overlap of input costs between different farm types it makes little sense to compare one to another. Where with outputs it is possible to say by comparison of the overall figure which region produces more crops or livestock for intermediate consumption to be relevant we must break it down further. For this reason you will find a more detailed breakdown for each of the ITL1 regions linked below:

*   [TLC - The North East](LINK TO TIFF IN THE NORTH EAST OF ENGLAND)

*   [TLD - The North West](LINK TO TIFF IN THE NORTH WEST OF ENGLAND)

*   [TLE - Yorkshire and The Humber](LINK TO TIFF IN YORKSHIRE AND THE HUMBER)

*   [TLF - The East Midlands](LINK TO TIFF IN THE EAST MIDLANDS OF ENGLAND)

*   [TLG - The West Midlands](LINK TO TIFF IN THE WEST MIDLANDS OF ENGLAND)

*   [TLH - The East of England](LINK TO TIFF IN THE EAST OF ENGLAND)

*   [TLIJ - London and the South East](LINK TO TIFF IN LONDON AND THE SOUTH EAST OF ENGLAND)

*   [TLK - The South West](LINK TO TIFF IN THE SOUTH WEST OF ENGLAND)

```{r saving files, eval = params$run == 'Figures', include = FALSE}
source(here('TIFF in the regions of England in 2021', 'scripts', 'saving_files_regional.R'))
```

```{r saving the text file, eval = params$run == 'Text', include = FALSE}
file_copy(here("TIFF in the regions of England in 2021", "TIFF-in-the-regions-of-England-in-2021_govspeak.md"),
          here("TIFF in the regions of England in 2021", "send to publishing"))

file.rename(here("TIFF in the regions of England in 2021", "send to publishing",
                 "TIFF-in-the-regions-of-England-in-2021_govspeak.md"),
            here("TIFF in the regions of England in 2021", "send to publishing",
                 glue("regional_tiff_regional_main_{date_pub}.txt")))

file_copy(here("TIFF in the regions of England in 2021", "TIFF-in-the-regions-of-England-in-2021.html"),
          here("TIFF in the regions of England in 2021", "send to publishing"))

file.rename(here("TIFF in the regions of England in 2021", "send to publishing",
                 "TIFF-in-the-regions-of-England-in-2021.html"),
            here("TIFF in the regions of England in 2021", "send to publishing",
                 glue("stats_notice_example_regional_main.html")))
```

## Section 4 - About these statistics

#### 4.1 Contact details

$C
Tim Buttanshaw 
<farmaccounts@defra.gov.uk>  
Telephone: 020 8026 3601  
Media enquiries: 0345 051 8486
Public enquiries: 0845 601 3034
$C

$A
Horizon House
Deanery Road
Bristol
BS1 5AH
$A

#### 4.2 Methodology

TIFF refers to income generated by production within the agricultural industry, including subsidies. TIFF represents business profits and remuneration for work done by owners and other unpaid workers. It excludes changes in the values of assets and stocks due to price changes, but includes non-agricultural activities such as further processing or tourist activities where these cannot be separated from the agricultural business. TIFF is the preferred measure of aggregate income for the agricultural industry, conforming to internationally agreed national accounting principles required by the UK National Accounts.

Values for the regions of England are derived by applying a factor to the England account for each of the regions, which is calculated using the June Survey data, to aportion the correct amount of the total Engaland value to each region. Latest account information for England can be found at [England: Total Income from Farming statistics](https://www.gov.uk/government/statistics/total-income-from-farming-in-england).

The England level estimates used as a starting point for the estimates in this release were published by Defra on 01 July 2022.

#### 4.3 Revisions

* Due to the lack of availability of data for Direct payments, the methodology for apportioning them has, for this release, been changed to calculate it from land area which has been shown to correlate well with payments data. This means that Direct Payments data in this release is not directly comparable to that of previous releases.

Revisions are intended to increase the precision of the estimates and are routinely the result of more data becoming available over time. Sometimes additional revisions are necessary to refine the methodology or correct historical errors.

TIFF is the relatively small difference between two large numbers and is therefore sensitive to small percentage changes in the values of Outputs and Intermediate Consumption. A combination of a revision downwards in Output and revision upwards in Intermediate Consumption leads to more sizeable revisions in percentage terms to GVA and TIFF.

Further information can be found on the webpage for [Defra’s policy statement on revisions and correction](https://www.gov.uk/government/publications/defra-policy-statement-on-revisions-and-corrections/defra-policy-statement-on-revisions-and-corrections).


#### 4.4 Summary quality report

A summary quality report for this statistical release can be found on the GOV.UK website for Aggregate agricultural accounts.
This is an overview note which is not release specific and was last updated in March 2019. It pulls together key qualitative information on the various dimensions of quality as well as providing a summary of methods used to compile the output. It relates to estimates of Total Income from Farming and aims to provide users with information on usability and fitness for purpose of these estimates.


#### 4.5 Quality assurance

DEFRA has in place quality assurance processes to check the accuracy and reliability of the aggregate agricultural accounts that include:

*   Ongoing review of methods employed in the calculation of the accounts.

*   Assessment of the quality of the estimates of the accounts with experts within DEFRA.

*   Discussion of the accounts with external experts.


#### 4.6 Development areas

DEFRA statisticians carry out a continuous review of methods employed in making estimates of the production and income accounts. This may lead to revisions to data series owing to improvements in methods, in addition to the use of more up-to-date information.

#### 4.7 Main users and uses of these statistics

The aggregate agricultural accounts are used both within government and by the wider agricultural industry in conjunction with other economic information to:

*   Monitor the productivity and competitiveness of the farming industry.

*   Inform policy decisions and to help monitor and evaluate current policies relating to agriculture in the UK by Government.

*   Inform stakeholders of the performance of the agricultural industry.

*   Inform research into the economic performance of the agricultural industry.


#### 4.8 User engagement

As stated at the start of this release, part of our ongoing commitment to compliance with the Code of Practice for Official Statistics, is to strengthen our engagement with users of these statistics and better understand the use made of them as well as the types of decisions that they inform. Thus, we invite users to make themselves known, to advise us of the use they do, or might, make use of these statistics, and what their wishes are in terms of engagement. Feedback on this notice and inquiries about these statistics is also welcomed. Please complete [this feedback form](https://forms.gle/YRxFut32k5xVamW67) to tell us how you use this statistical notice.

If you have any other feedback you wish to provide, please get in contact using the details provided in the 'What you need to know about his release' section.

#### 4.9 Future publications

These estimates for `r working_year` will be subject to minor (unless otherwise specified) revisions in future publications of TIFF in the regions of England where the availability of additional data and revised data will be incorporated to improve the accuracy of the estimates.

To find out the latest information on when UK government statistics will be released, go to the gov.uk Research and statistics webpage and select ‘Statistics (up-coming)’.


#### 4.10 Other publications relevant to this release

A number of publications released by DEFRA, are relevant to this release. Below is a list of the key publications and links to them on GOV.UK

*   [Total Income from Farming in the UK](https://www.gov.uk/government/statistics/total-income-from-farming-in-the-uk)

*   [Total Income from Farming in England](https://www.gov.uk/government/statistics/total-income-from-farming-in-england)

*   [Farm Business Survey: Farm Business Income](https://www.gov.uk/government/collections/farm-business-survey)

---

*[TIFF]: Total Income from Farming
*[GVA]: Gross Value Added
[^1]: The ITL1 regions for Greater London and the South East have been combined due to the fact that London has such a small farming infrastructure
